material and methods

### 2017-09-17 man/ms_1_material_methods.Rmd
update

EVI data consits of 16-day maximun value composite images (23 per year) of the EVI value with a spatial resolution of 231 m x 231 m. We selected the pixels covering the distribution of *Q. pyrenaica* forests in Sierra Nevada (*n* = 928 pixels). MODIS EVI Data from Collection 6 were obtanied using Google Earth Engine platform for the period 2000 - 2016.

OJITO---------- reescribir esto

A quality filter was applied to select only valid values of EVI.

First we used information from the Quality Assesment band (QA band) to filter out those values affected by high content of aerosols, clouds, shadows, snow or water;

snow, ice, cloud

@@

EVI data were

>>>>

EVI data consits of 16-day maximun value composite images (23 per year) of the EVI value with a spatial resolution of 250 m x 250 m. We selected the pixels covering the distribution of *Q. pyrenaica* forests in Sierra Nevada (*n* = 928 pixels). MODIS EVI Data from Collection 6 were obtanied using Google Earth Engine platform for the period 2000 - 2016. A data filtering was applied to select EVI valid values. The filtering was done using quality flags and VI Usefulness Indices accompanying the EVI data. We filter out those values affected by high content of aerosols, clouds, shadows, snow or water.

@@
